Analysing the effect of land-use type on the proportion of scouts

### 2022-06-29 analysis/landuse_effect_jackknife.Rmd
updated the code to use proportion of recruits rather than proportion of scouts, this was we can more easily compare landscape type with a measure of waggle dance use

>>>>

```{r, convert_p}

ms_mr <- read.csv(file = "data/site_ms_mr.csv")

urban_lu <- urban_lu %>%
  # inner_join(ms_mr, by = "site") %>%
  # select(-ms, -mr, -p.y) %>%
  # rename(p = p_trips) %>%
  # mutate(p = ifelse(p.x == 1, 1, p)) %>%
  mutate(p = 1-p)
  # select(site, p, 3:10)

rural_lu <- rural_lu %>%
  # inner_join(ms_mr, by = "site") %>%
  # select(-ms, -mr, -p.y) %>%
  # rename(p = p_trips) %>%
  # mutate(p = ifelse(p.x == 1, 1, p)) %>%
  mutate(p = 1-p)
  # select(site, p, woodland, 3:12)

### 2022-06-29 analysis/landuse_effect_prop_scouts.Rmd
updated the code to use proportion of recruits rather than proportion of scouts, this was we can more easily compare landscape type with a measure of waggle dance use

@@

# make model fit graph of pc1 against prop scouts and mark the sites
ar_fit <- ggplot(
  data = ar_sortedpropscouts, aes(x = Comp_.1, y = prop_scouts)
) +
  geom_point() +
  geom_line(data = rural_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = rural_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  geom_point(
    data = ar_marked, aes(x = Comp_.1, y = prop_scouts, colour = "red")
  ) +
  geom_text(
    data = ar_marked, aes(x = Comp_.1, y = prop_scouts, label = site),
    nudge_x = c(0, 0), nudge_y = c(-0.05, 0.05), size = rel(textsize)
  ) +
  theme_classic() +
  theme(legend.position = "none", text = element_text(size = rel(textsize - 2))) +
  xlab("PC 1") +
  ylab("Estimated proportion of scouts")

@@

# make model fit graph of pc1 against prop scouts and mark the sites with the
# lowest, middle and highest proportion of scouts
u_fit <- ggplot(
  data = u_sortedpropscouts, aes(x = Comp_.1, y = prop_scouts)
) +
  geom_point() +
  geom_point(
    data = u_marked, aes(x = Comp_.1, y = prop_scouts, colour = "red")
  ) +
  geom_text(
    data = u_marked, aes(x = Comp_.1, y = prop_scouts, label = site),
    nudge_x = c(0, 0), nudge_y = c(-0.05, 0.05), size = rel(textsize)
  ) +
  geom_line(data = urban_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = urban_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  theme_classic() +
  theme(legend.position = "none", text = element_text(size = rel(textsize - 2))) +
  xlab("PC 1") +
  ylab("Estimated proportion of scouts")

>>>>

```{r, convert_p}

ms_mr <- read.csv(file = "data/site_ms_mr.csv")

urban_lu <- urban_lu %>%
  # inner_join(ms_mr, by = "site") %>%
  # select(-ms, -mr, -p.y) %>%
  # rename(p = p_trips) %>%
  # mutate(p = ifelse(p.x == 1, 1, p)) %>%
  mutate(p = 1-p)
  # select(site, p, 3:10)

rural_lu <- rural_lu %>%
  # inner_join(ms_mr, by = "site") %>%
  # select(-ms, -mr, -p.y) %>%
  # rename(p = p_trips) %>%
  # mutate(p = ifelse(p.x == 1, 1, p)) %>%
  mutate(p = 1-p)
  # select(site, p, woodland, 3:12)

```

@@

# make model fit graph of pc1 against prop scouts and mark the sites
ar_fit <- ggplot(
  data = ar_sortedpropscouts, aes(x = Comp_.1, y = prop_scouts)
) +
  geom_point() +
  geom_line(data = rural_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = rural_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  geom_point(
    data = ar_marked, aes(x = Comp_.1, y = prop_scouts, colour = "red")
  ) +
  geom_text(
    data = ar_marked, aes(x = Comp_.1, y = prop_scouts, label = site),
    nudge_x = c(0, 0), nudge_y = c(-0.05, 0.05), size = rel(textsize)
  ) +
  theme_classic() +
  theme(legend.position = "none", text = element_text(size = rel(textsize - 2))) +
  xlab("PC 1") +
  ylab("Estimated waggle dance use")

@@

# make model fit graph of pc1 against prop scouts and mark the sites with the
# lowest, middle and highest proportion of scouts
u_fit <- ggplot(
  data = u_sortedpropscouts, aes(x = Comp_.1, y = prop_scouts)
) +
  geom_point() +
  geom_point(
    data = u_marked, aes(x = Comp_.1, y = prop_scouts, colour = "red")
  ) +
  geom_text(
    data = u_marked, aes(x = Comp_.1, y = prop_scouts, label = site),
    nudge_x = c(0, 0), nudge_y = c(-0.05, 0.05), size = rel(textsize)
  ) +
  geom_line(data = urban_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = urban_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  theme_classic() +
  theme(legend.position = "none", text = element_text(size = rel(textsize - 2))) +
  xlab("PC 1") +
  ylab("Estimated waggel dance use")
